\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-31 OaklandSubmission/related.tex
Spelling in related

\tool falls into the category of frameworks that compile high level languages to \mpc protocols. We discuss other such frameworks next.
%Existing \mpc tools work with either a high or a low level desciption of the functionalities to be implemented securely.
 %\end{enumerate}
%\noindent\textbf{Generating \mpc protocols.}
%There has been vast literature on the generation of \mpc protocols. These works all provide tools at various levels of abstraction that help a programmer generate cryptographic protocols for various functionalities. These levels can be classified as follows: 
%Examples of tools in the former category include the following: 
Fairplay's Secure Function Definition Language (SFDL)~\cite{fairplay,fairplaymp} and CBMC-GC~\cite{cbmcgc} compile C or Pascal like programs into boolean circuits that are then evaluated using garbled circuits~\cite{yao}.
ObliVM~\cite{oblivm} protects access patterns using an oblivious RAM~\cite{oram1,oram2} and also uses garbled circuits for compute.
In Secure Multiparty Computation Language (SMCL)~\cite{smcl},  Java like programs are compiled into arithmetic circuits that are then evaluated using the VIFF framework~\cite{viff}. Wysteria~\cite{wysteria} compiles  programs into boolean circuits and uses a GMW-based backend~\cite{choi,gmw}. 
 Mitchell {\em et al.}~\cite{lambdaps} allow the user to select between Shamir's secret sharing~\cite{sss} and fully homomorphic encryption~\cite{gentry}.  Unlike \tool, all these tools use either a arithmetic backend or a boolean backend but not a combination of both.

@@

%\\\\
%\noindent\textbf{Custom \mpc protocols.} 
Many works have designed specialized, hand-crafted protocols for various \mpc tasks. 
%The reason for doing this was to allow for a mix between arithmetic and boolean computations as a secure computation protocol for a pure boolean circuit would have been very inefficient. 
This process require deep knowledge of cryptography
to ensure that the protocols are secure.
Examples include privacy-preserving classification of medical ElectroCardioGram (ECG)~\cite{barni}, iris and fingerprint recognition~\cite{blanton}, remote diagnostics~\cite{brickell}, private sequence analysis~\cite{franz}, private biometric identification~\cite{huang}, privacy-preserving matrix factorization and ridge-regression~\cite{valeriaMatrix, valeriaRidge}, machine-learning classification~\cite{shafindss}, decision trees and forests~\cite{wu}, neural network training~\cite{secureml} and prediction~\cite{minionn}.
% As seen from our experiments, the protocols generated by \tool give us better or comparable execution times as many of the above works with minimal programmer overhead. %\nc{What do we want to say here exactly?}

>>>>

\tool falls into the category of frameworks that compile high level languages to \mpc protocols. We discuss other such frameworks next.
%Existing \mpc tools work with either a high or a low level desciption of the functionalities to be implemented securely.
 %\end{enumerate}
%\noindent\textbf{Generating \mpc protocols.}
%There has been vast literature on the generation of \mpc protocols. These works all provide tools at various levels of abstraction that help a programmer generate cryptographic protocols for various functionalities. These levels can be classified as follows: 
%Examples of tools in the former category include the following: 
Fairplay's Secure Function Definition Language (SFDL)~\cite{fairplay,fairplaymp} and CBMC-GC~\cite{cbmcgc} compile C or Pascal like programs into boolean circuits that are then evaluated using garbled circuits~\cite{yao}.
ObliVM~\cite{oblivm} protects access patterns using an oblivious RAM~\cite{oram1,oram2} and also uses garbled circuits for compute.
In Secure Multiparty Computation Language (SMCL)~\cite{smcl},  Java like programs are compiled into arithmetic circuits that are then evaluated using the VIFF framework~\cite{viff}. Wysteria~\cite{wysteria} compiles  programs into boolean circuits and uses a GMW-based backend~\cite{choi,gmw}. 
 Mitchell {\em et al.}~\cite{lambdaps} allow the user to select between Shamir's secret sharing~\cite{sss} and fully homomorphic encryption~\cite{gentry}.  Unlike \tool, all these tools use either an arithmetic backend or a boolean backend but not a combination of both.

@@

%\\\\
%\noindent\textbf{Custom \mpc protocols.} 
Many works have designed specialized, hand-crafted protocols for various \mpc tasks. 
%The reason for doing this was to allow for a mix between arithmetic and boolean computations as a secure computation protocol for a pure boolean circuit would have been very inefficient. 
This process requires deep knowledge of cryptography
to ensure that the protocols are secure.
Examples include privacy-preserving classification of medical ElectroCardioGram (ECG)~\cite{barni}, iris and fingerprint recognition~\cite{blanton}, remote diagnostics~\cite{brickell}, private sequence analysis~\cite{franz}, private biometric identification~\cite{huang}, privacy-preserving matrix factorization and ridge-regression~\cite{valeriaMatrix, valeriaRidge}, machine-learning classification~\cite{shafindss}, decision trees and forests~\cite{wu}, neural network training~\cite{secureml} and prediction~\cite{minionn}.
% As seen from our experiments, the protocols generated by \tool give us better or comparable execution times as many of the above works with minimal programmer overhead. %\nc{What do we want to say here exactly?}
